Recruiting Chapter

### 2021-05-04 educ250c_presentation.Rmd
switch PDFs to PNGs for educ250c

```{r event-count-figure-pubu, echo = FALSE}
knitr::include_graphics('assets/figures/plot_event_count_pubu.pdf')
```

<br>
<br>

@@

```{r event-count-figure-privu, echo = FALSE}
knitr::include_graphics('assets/figures/plot_event_count_privu.pdf')
```

<br>
<br>

@@

```{r, echo = FALSE}
knitr::include_graphics('assets/figures/figure_5.pdf')
```

@@

```{r ego-network-figure-privu, echo = FALSE}
knitr::include_graphics('assets/figures/ego_network_figure_privu.pdf')
```

@@

```{r ego-network-figure-pubu, echo = FALSE}
knitr::include_graphics('assets/figures/ego_network_figure_pubu.pdf')
```

@@

```{r plot-1mode-pubu, echo = FALSE}
knitr::include_graphics('assets/figures/plot_1mode_pubu.pdf')
```

@@

```{r plot-1mode-all-pubu-outst, echo = FALSE}
knitr::include_graphics('assets/figures/plot_1mode_all_pubu_outst.pdf')
```

>>>>

```{r event-count-figure-pubu, echo = FALSE}
# knitr::include_graphics('assets/figures/plot_event_count_pubu.pdf')
knitr::include_graphics('assets/figures/plot_event_count_pubu.png')
```

@@

```{r event-count-figure-privu, echo = FALSE}
# knitr::include_graphics('assets/figures/plot_event_count_privu.pdf')
knitr::include_graphics('assets/figures/plot_event_count_privu.png')
```

@@

```{r, echo = FALSE}
# knitr::include_graphics('assets/figures/figure_5.pdf')
knitr::include_graphics('assets/figures/figure_5.png')
```

@@

```{r ego-network-figure-privu, echo = FALSE}
# knitr::include_graphics('assets/figures/ego_network_figure_privu.pdf')
knitr::include_graphics('assets/figures/ego_network_figure_privu.png')
```

@@

```{r ego-network-figure-pubu, echo = FALSE}
# knitr::include_graphics('assets/figures/ego_network_figure_pubu.pdf')
knitr::include_graphics('assets/figures/ego_network_figure_pubu.png')
```

@@

```{r plot-1mode-pubu, echo = FALSE}
# knitr::include_graphics('assets/figures/plot_1mode_pubu.pdf')
knitr::include_graphics('assets/figures/plot_1mode_pubu.png')
```

@@

```{r plot-1mode-all-pubu-outst, echo = FALSE}
# knitr::include_graphics('assets/figures/plot_1mode_all_pubu_outst.pdf')
knitr::include_graphics('assets/figures/plot_1mode_all_pubu_outst.png')
```
